### 2016-01-21 AssignmentIX/Assignment9-Ditz_Schroeder-WS15-16.tex
final

\section*{Theoretical Assignment - \textit{Overlap and Layout}}

\section*{Theoretical Assignment - \textit{Overlap graph figure}}

>>>>

\section*{Theoretical Assignment - \textit{Overlap and Layout}}
\subsection*{graphs}
The graphs from the exercise are shown in Figure 1-2. Figure \ref{fig:og} is the overlap grap with minimal spanning tree (red edges) and Figure \ref{fig:layout} shows the layout.

\begin{figure}[h]
	\includegraphics[width=\textwidth]{minimal-Spanning-Tree.png}
	\caption{Minimal-spanning-tree}
	\label{fig:og}
\end{figure}

\begin{figure}[h]
	\includegraphics[width=\textwidth]{layout.png}
	\caption{layout}
	\label{fig:layout}
\end{figure}

\subsection*{Is the Layout consitent?}
One overlap ($f_6$ and $f_8$) is not consistent, because:
\begin{equation*}
o(3'f_6 - 3'f_8)=80
\end{equation*}
\section*{Theoretical Assignment - \textit{Overlap graph figure}}

A Figure for a paper would look like Figure \ref{fig:paper}.

\begin{figure}[h]
	\centering
	\subfigure{
		\includegraphics[width=0.45\textwidth]{minimal-Spanning-Tree.png}
	}
	\subfigure{
		\includegraphics[width=0.45\textwidth]{layout.png}
	}
	\caption{\textbf{left}: Overlap Graph with minimal spanning tree in red. \textbf{right}: Layout computed with the minimal spanning tree shown on the left site.}
	\label{fig:paper}
\end{figure}

### 2016-01-21 AssignmentX/Assignment10-Ditz_Schroeder-WS15-16.tex

\begin{document}
%\header{Blatt}{Tutor}{Abgabedatum}{Vorlesung}{Bearbeiter}{Semester}{Anzahl Aufgaben}
\header{11}{Alexander Seitz}{18. January 2016}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{2}

@@

\begin{align}
 S_1 &= AACCGTTAACGTAAACGT \nonumber \\
 S_2 &= AACCGTAAACGTTAACGT \nonumber \\
 S_3 &= AACCGTTAAACGTAACGT \nonumber \\
 S_4 &= AACCGTAACGTTAAACGT \nonumber
\end{align}

This happens due to the fact that there are nodes with more than one outgoing an incoming edge. If
one chooses $k = 5$ the resulting de Bruijn graph would look like the graph in Figure \ref{fig:5mere}.
It is obvious that the number of nodes is depended on $k$. With a bigger $k$ there are more nodes in 
the resulting de Bruijn graph. But in this case there is one problem. Since there are more than two 
unbalanced nodes in the de bruijn graph there is no Eulerian path.

\begin{figure}[h]
 \centering
 \includegraphics[width=0.7\textwidth]{deBruijnGraph_4mere.png}
 \caption{De Bruijn graph for the given reads and $k = 4$.}
 \label{fig:4mere}
\end{figure}

>>>>

\begin{document}
%\header{Blatt}{Tutor}{Abgabedatum}{Vorlesung}{Bearbeiter}{Semester}{Anzahl Aufgaben}
\header{10}{Alexander Seitz}{18. January 2016}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{2}

@@

\begin{align}
 S_1 &= ACCGTTAACGTAAACGT \nonumber \\
 S_2 &= ACCGTAAACGTTAACGT \nonumber \\
 S_3 &= ACCGTTAAACGTAACGT \nonumber \\
 S_4 &= ACCGTAACGTTAAACGT \nonumber
\end{align}

This happens due to the fact that there are nodes with more than one outgoing an incoming edge. If
one chooses $k = 5$ the resulting de Bruijn graph would look like the graph in Figure \ref{fig:5mere}.
It is obvious that the number of nodes is depended on $k$. With a bigger $k$ there are more nodes in 
the resulting de Bruijn graph. The resulting graph for $k = 5$ is non-connected. So the superstring 
for this graph is not just one but three strings:

\begin{align}
 S_{part_1} &= TAAACTG \nonumber \\
 S_{part_2} &= CGTAACGTTAA \nonumber \\
 S_{part_3} &= ACCGT \nonumber
\end{align}

One can see that $S_{part_1} = f_5$ and $S_{part_3} = f_1$, while $S_{part_2}$ is the result of an 
overlap alignment between $f_2$, $f_3$ and $f_4$. In general the second graph is more realistic. 
It is very unlikely to get a connected graph with real-life data. So it is possible that just $f_2$, 
$f_3$ and $f_4$ come from the same area in the target DNA. $f_1$ and $f_5$ could come from a different 
contig and, hence, result in this graph (Figure \ref{fig:5mere}). Since this is a minimal example 
the first graph (Figure \ref{fig:4mere}) is not wrong but one should not expect to get a connected 
graph all the time. In fact a connected graph is suspicious, normally.

\begin{figure}[h]
 \centering
 \includegraphics[width=1\textwidth]{deBruijnGraph_4mere.png}
 \caption{De Bruijn graph for the given reads and $k = 4$.}
 \label{fig:4mere}
\end{figure}
